Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2017-11-07 aggregation/agg-review.tex
minor fixes

Partial aggregation is already used in practice to conceal private data, but current practices used to generate aggregated results from input model configurations do not provide a way for a reviewer to validate the aggregation.  If a study containing confidential information is split into public and private partitions as in Eq.~\ref{eqn:private} and Fig.~\ref{fig:private}, then the results of the computation can be validated directly by the reviewer.  To achieve this, the reviewer must be granted access to both the public and private partitions in order to confirm that the partitioning is valid according to Eq.~\ref{eqn:partition}, and that $\mathbf{b}_{priv}$ was computed correctly.  However, the private information used in the computation can still be withheld from the disclosure.

>>>>

Partial aggregation is already used in practice to conceal private data, but current methods do not provide a way for a reviewer to validate the result.  If a study containing confidential information is split into public and private partitions as in Eq.~\ref{eqn:private} and Fig.~\ref{fig:private}, then the results of the computation can be validated directly by the reviewer.  To achieve this, the reviewer must be granted access to both the public and private partitions in order to confirm that the partitioning is valid according to Eq.~\ref{eqn:partition}, and that $\mathbf{b}_{priv}$ was computed correctly.  However, the private information used in the computation can still be withheld from the disclosure.

### 2017-11-07 aggregation/agg-semantic.tex
minor fixes

Agreement about the meaning of concepts is often accomplished using linked semantic data \citep{Bizer_2009}, in which an object to be interpreted is signified by a link to a resource on the World Wide Web, typically referred to as a Uniform Resource Identifier (URI) or a hyperlink.  The resource at the end of the link functions as a point of agreement: both study author and data user can follow it from anywhere on the Internet to obtain the same information.  The content pointed to by the hyperlink, along with context provided by \emph{other} references to the same content, gives meaning to the information and allows it to be curated by the study authors and other members of the community \citep{Khan_2011}.   Semantic data are structured by reference to knowledge models called ontologies, which describe the relationships among different types of entities \citep{Madin2008}.  Some preliminary descriptions of the entity types involved in LCA computation, and their relationships to one another, have recently been developed \citep{Ciroth_Srocka_2014, Janowicz_WOP_2015, Kuczenski_JCP_2016}.

Before the goal of easily reproducible foreground models can be realized, the linked data foundation must be laid.  Background database providers should ensure that their users have access to \emph{stable semantic references} for publicly available datasets that denote a particular activity in a particular database version and configuration.  These references should take the form of URIs that can be accessed using any Internet browser and can provide both author and reader with documentary information describing the referred dataset, the available reference flows and their dimensions, and a mechanism for the reader to obtain access to the exchange data or LCI/LCIA computations for the purposes of model validation.  A dependency reference in disclosure item~\ref{itm:bg} should include both an activity and a reference flow.

>>>>

Agreement about the meaning of concepts is often accomplished using linked semantic data \citep{Bizer_2009}, in which an object to be interpreted is signified by a link to a resource on the World Wide Web, typically referred to as a Uniform Resource Identifier (URI) or a hyperlink.  The resource at the end of the link functions as a point of agreement: both study author and data user can follow it from anywhere on the Internet to obtain the same information.  The content pointed to by the hyperlink, along with context provided by \emph{other} references to the same content, gives meaning to the information and allows it to be curated by the study authors and other members of the community \citep{Khan_2011}.   %Semantic data are structured by reference to knowledge models called ontologies, which describe the relationships among different types of entities \citep{Madin2008}.  Some preliminary descriptions of the entity types involved in LCA computation, and their relationships to one another, have recently been developed \citep{Ciroth_Srocka_2014, Janowicz_WOP_2015, Kuczenski_JCP_2016}.

Before the goal of easily reproducible foreground models can be realized, this linked data foundation must be laid.  Background database providers should ensure that their users have access to \emph{stable semantic references} for publicly available datasets that denote a particular activity in a particular database version and configuration.  These references should take the form of URIs that can be accessed using any Internet browser and can provide both author and reader with documentary information describing the referred dataset, the available reference flows and their dimensions, and a mechanism for the reader to obtain access to the exchange data or LCI/LCIA computations for the purposes of model validation.  A dependency reference in disclosure item~\ref{itm:bg} should include both an activity and a reference flow.
